### 2025-11-06 simulation.qmd
20251106 - Monte Carlo simulation

Monte Carlo simulation involves repeated random sampling from a known distribution [@Sigal2016].
For instance, if we know the population distribution for the likely outcomes for a player—e.g., a normal distribution with a known mean (e.g., 150 points) and standard deviation (e.g., 20 points)—we can repeatedly sample randomly from this distribution.
The distribution could be, as examples, a normal distribution, a log-normal distribution, a binomial distribution, a chi-square distribution, etc. [@Sigal2016].
The distribution provides a probability density function, which indicates the probability that any particular value would be observed if the data arose from that distribution.

@@

1. generate the data for the simulation from the relevant probabilty distribution(s)
1. analyze the simulated data
1. summarize the results across the simulation replications

>>>>

Monte Carlo simulation is named after the Casino de Monte-Carlo in Monaco because Monte Carlo simulations involve random samples (random chance), as might be found in casino gambling.
Monte Carlo simulation involves repeated random sampling from a known distribution [@Sigal2016].
For instance, if we know the population distribution for the likely outcomes for a player—e.g., a normal distribution with a known mean (e.g., 150 points) and standard deviation (e.g., 20 points)—we can repeatedly sample randomly from this distribution.
The distribution could be, as examples, a normal distribution, a log-normal distribution, a binomial distribution, a chi-square distribution, etc. [@Sigal2016].
The distribution provides a probability density function, which indicates the probability that any particular value would be observed if the data arose from that distribution.

@@

1. generate the data for the simulation from the relevant probability distribution(s)
1. analyze the simulated data
1. summarize the results across the simulation replications
